Models

### 2022-09-19 analysis/05_model_metrics.Rmd
get what we need from the slope summaries

Summaries of study slopes
```{r}
#First - how many studies had a significant trend for each metric? 
study_slopes %>% 
  filter(sig == TRUE) %>% 
  filter(metric %in% c("SES_FRic", "SES_FEve", "SES_FDiv", "Jaccard_base", "S")) %>% 
  group_by(metric) %>% 
  summarise(n_study_id = n_distinct(study_id)) %>%
  mutate(percent = n_study_id/53)

#And which studies were they?
study_slopes %>% 
  filter(sig == TRUE) %>% 
  filter(metric %in% c("SES_FRic", "SES_FEve", "SES_FDiv", "Jaccard_base", "S")) %>% 
  select(study_id, metric) %>%
  distinct()

@@

study_slope_data <- study_slopes %>%
  dplyr::select(study_id, metric, estimate) %>%
  left_join(meta %>% 
              dplyr::select(-rarefyid) %>% 
              distinct() %>%
              mutate(study_id = as.character(study_id))) %>%
  left_join(model_data %>% dplyr::select(study_id, startyear, duration) %>% distinct())

>>>>

Summaries of study slopes
```{r}
#First - how many studies had a significant trend for each metric? 
study_slopes %>% 
  filter(sig == TRUE) %>% 
  filter(metric %in% c("SES_FRic", "SES_FEve", "SES_FDiv", "Jaccard_base", "S")) %>% 
  mutate(positive = ifelse(estimate > 0, TRUE, FALSE)) %>%
  group_by(metric, positive) %>% 
  summarise(n_study_id = n_distinct(study_id))

#And which studies were they?
study_slopes %>% 
  filter(sig == TRUE) %>% 
  filter(metric %in% c("SES_FRic", "SES_FEve", "SES_FDiv", "Jaccard_base", "S", "FRic", "FEve", "FDiv")) %>% 
  select(study_id, metric) %>%
  distinct()

@@

study_slope_data <- study_slopes %>%
  dplyr::select(study_id, metric, estimate) %>%
  left_join(meta %>% 
              mutate(study_id = as.character(study_id))) %>%
  left_join(model_data %>% dplyr::select(study_id, startyear, duration) %>% distinct())
